Extended Data

### 2021-11-16 doc/manuscript/Dow_Extended_Data.Rmd
review extended data fig 3

![**Extended Data Figure 3 | Landscapes of relationships between the day of year on which 25% of annual growth is achieved ($DOY_{25}$) and temperature in prior weeks for ring- and diffuse-porous trees at the Smoithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** Shown are matrices of linear coefficients of first-order linear regressions between temperature and $DOY_{25}$, where Window Open and Window Close indicate number of weeks prior to $DOY_{25}$ (ring-porous: May 5 at SCBI, May 13 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black circles indicate the critical $T_{max}$ window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF).](tables_figures/climwin_figure.png){ width=70% }

>>>>

![**Extended Data Figure 3 | Landscapes of relationships between the day of year on which 25% of annual growth is achieved ($DOY_{25}$) and temperature in prior weeks for ring- and diffuse-porous trees at the Smoithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** Shown are matrices of $\beta$ coefficients from first-order linear regressions between mean maximum temperature ($T_{max}$) and $DOY_{25}$. Window Open and Window Close indicate number of weeks prior to $DOY_{25}$ (listed in `r EDT_phenology_parameters`). Yellow shading indicates neutral relationships, while orange or red shading indicates that $DOY_{25}$ advances with increased $T_{max}$ over the given time window (negative $\beta$). Black circles indicate the critical temperature window selected based on minimization of $\Delta AICc$, the difference in Akaike Information Criterion corrected for small sample size relative to a null model. Critical temperature windows are listed in `r EDT_phenology_parameters`.](tables_figures/climwin_figure.png){ width=70% }
